Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-08 article.rnw
Change the bin width on the AIC histogram to 2.
Per Hao Ran's suggestion, to ease reading of "significantly different"
AIC values.

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		hist(brute_data$statistics[[ic]],
			main="",
			xlab=ic_name,
			xaxs='i',
			yaxs='i',
			ylim=c(0,6000)
		)
		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="purple")
	@
	\end{subfigure}

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		get_breaks <- function(x, bin_width) {
			lower_bound <- min(x) - min(x)%%bin_width
			upper_bound <- max(x) + (bin_width - max(x)%%bin_width)%%bin_width
			return(seq(lower_bound, upper_bound, by = bin_width))
		}
		hist(brute_data$statistics[[ic]],
			main="",
			xlab=ic_name,
			xaxs='i',
			yaxs='i',
			ylim=c(0,2500),
			breaks=get_breaks(brute_data$statistics[[ic]], 2)
		)
		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="purple")
	@
	\end{subfigure}
